\vspace{-2cm} \LARGE Divergence-Free Smoothed Particle Hydrodynamics \\ \large Advanced Simulation and Visualization of Fluids in Computer Graphics

### 2016-12-15 report/paper.tex
dirichlet boundary conditions

\subsection{Screen space fluid rendering}

>>>>

\subsection{Boundary conditions}
Dirichlet boundary condition was implemented in order to simulate the fluid inside a bounding box. Dirichlet assumes that the pressure is zero outside the fluid which and therefore the value a quantity has to take along the boundary has to be specified, in this case the velocity was set to zero when a particle reaches the boundary, Bridson~\cite{bridson}.
